The transition redshift as a probe of reionization

### 2019-08-12 paper/ms.tex
Add beginning of detectability section

\section{Detectability}

>>>>

\section{Detectability}
Up to this point, we have not been specific about which galactic emission line
one might consider using to measure \zst{}. This is because computing \zst{}
from our simulations with our simple line intensity model
(\S~\ref{ssec:oiii_int_map}) does not require specifying the total average
intensity of the field.

The variance of the cross-spectrum between the 21~cm field and a line $i$ is given by \citep[e.g.][]{2007ApJ...660.1030F}
\beq \label{eq:var_xps}
\text{Var}\left[P_{21,i}\right] = P_{21,i}^2 + P_{21,\text{tot}} P_{i,\text{tot}}\text{,}
\eeq
where $P_{21,\text{tot}} = P_{21,21} + N_{21}$, where $N_{21}$ is the total
noise contribution, and is similarly defined for $P_{i,\text{tot}}$.
